%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    author(s): RoboCupAtHome Technical Committee(s)
%%  description: Introduction
%%
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
\label{chap:introduction}


\section{RoboCup}
\label{sec:introduction:robocup}
\RoboCup{} is an international joint project to promote AI, robotics, and related fields. It is an attempt to foster AI and intelligent robotics research by providing standard problems where a wide range of technologies can be integrated and examined. More information can be found at:
{\small\url{http://www.robocup.org/}}.


\section{RoboCup@Home}
\label{sec:introduction:robocupathome}
The \AtHome{} league aims to develop service and assistive robot technology with high relevance for future personal domestic applications. It is the largest international annual competition for autonomous service robots and is part of the \RoboCup{} initiative. A set of benchmark tests is used to evaluate the robots' abilities and performance in a realistic non-standardized home environment setting. Focus lies on the following domains but is not limited to: \HRI{} and Cooperation, \NAV{} and \MAP{} in dynamic environments, \CV{} and \OR{} under natural lighting conditions, Object \MAN{}, \AB{}, \BI{}, \AmI{}, Standardization and \SysI{}. It is collocated with the \RoboCup{} symposium.

\section{RoboCup Brazil Open}
\label{sec:introduction:RBO}

The RoboCup Brazil Open @Home Virtual competition aims to develop service and assistive robot technology with high relevance for future personal domestic applications. It is the largest international annual competition for autonomous service robots and is part of the RoboCup initiative. A set of benchmark tests is used to evaluate the robots’ abilities and performance in a virtual home environment setting. Focus lies on the following domains but is not limited to: Navigation and Mapping in virtual environments, Computer Vision and Object Recognition, Object Manipulation, Adaptive Behaviors, Behavior Integration, Ambient Intelligence, Standardization and System Integration. 

\input{chapters/introduction/Organization}

% \input{chapters/introduction/Infrastructure}

% \input{chapters/introduction/Leagues}

\input{chapters/introduction/Competition}

% \input{chapters/introduction/Awards}

% Local Variables:
% TeX-master: "Rulebook"
% End:
