\section{Receptionist [Party Host]}
\label{test:receptionist}
\subsection*{Description}
The robot has to take new guests to the living room to introduce them and offer a free place to sit.\\
    
\textbf{Main goal:}
    Introduce newcomers to a party and maintain appropriate gaze direction (at person, direction of navigation).

% \vspace{-5pt}
\textbf{Optional goals:}
\begin{enumerate}[nosep]
	\item Open the entrance door for each arriving guest.
	\item Describe the guest for the other people.
\end{enumerate}

\subsection*{Focus}
\SysI{}, \HRI{}, \PerDet{}, \PerRec
% human detection and recognition, safe navigation and human-robot interaction with unknown people.

\subsection*{Setup}
\begin{itemize}
	\item \textbf{Location}: 
	\begin{itemize}
	\item The test takes place in the living room.	
	\item The robot starts inside the \Arena{} at a predefined location near the entrance door.
	\item \textbf{Entrance:} The entrance door is open by default. The team leader can request to close the door to score additional points by opening it for the guests.
	\end{itemize}
	
	\item \textbf{People:} 
	\begin{itemize}
	\item \textbf{Host:} The host's name and favorite drink will be announced before the test. The host is already sitting in the living room. the robot knows the host.

	\item \textbf{Guests:} The guests have a name and favorite drink. An arriving guest will either step in front of the robot or ring the bell if the door is closed. Guests have to be guided to the living room to be introduced. Each of the guest will arrive separately. 
    % The sound of the bell will be provided to teams during setup period before competition.
	\end{itemize}

\end{itemize}

\subsection*{Procedure}
\begin{itemize}
    \item \textbf{Introductions:} When introducing guests, the robot must clearly identify the person being introduced and state their name and favorite drink. Introducing two people means to introduce them to each other.
	
	\item \textbf{Seating People:} The robot must point at a place or location where the guest can sit.
	
	\item \textbf{Switching Places:} Guests may switch places after they were seated.
	
	\item \textbf{Describing the First Guest:} Naming at least 4 characteristics of the first guest, i.e., color of clothes, color of hair.
	\item \textbf{Looking at person/direction of navigation:} During verbal interactions and descriptions of people, robot looks at the conversational partner. Robot can point at the person being introduce/described or alternate gaze between two people. During navigation robot looks in the direction where it is going.  
\end{itemize}

\subsection*{Additional rules and remarks}
\begin{enumerate}[nosep]
	\item \textbf{Misunderstanding:} Not understanding the guests and asking them again is fine.
	\item \textbf{Offer a seat:} The instructions for the seat must be clear (do not point to the void).
			
\end{enumerate}


\subsection*{Instructions}

\subsubsection*{To Referee}

The referees need to:
\begin{itemize}
	\item Assign name and drink to 3 volunteers.
	\item Arrange (and re-arrange) people in the living room.
	\item Open the door when requested by the robot.
\end{itemize}

\subsubsection*{To OC}

During setup day:
\begin{itemize}
	\item Provide the dorbell sound.
\end{itemize}

2h before test:
\begin{itemize}
	\item Announce starting position.
	\item Announce host's name and favorite drink.
	\item Recruit volunteers as host and guests.
\end{itemize}

% \newpage
\subsection*{Score sheet}
The maximum time for this test is 8 minutes.

\begin{scorelist}[startbutton=false]
	\scoreheading{Main Goal}
	\scoreitem[3]{150}{Introduce the new guest to every other guest (Say guest's correct name)}
	\scoreitem[3]{100}{Say guest's correct drink}
	\scoreitem[3]{200}{Offer a seat to the new guest (if available)}
%	\scoreitem[3]{100}{Point at the person talking (base, manipulator or face direction)}
	\scoreitem[3]{100}{Point at the person being described (base, manipulator or face direction)}

 	\scoreheading{Regular Penalties}

	\penaltyitem[3]{200}{Offer a seat already taken}
	% \penaltyitem[2]{50}{Persistent inappropriate gaze - away from conversational partner}
	% \penaltyitem[1]{50}{Persistent gaze not in the direction of the navigation while moving}

	\scoreheading{Bonus Rewards}
	\scoreitem[3]{100}{Open the entrance door for a guest}
	\scoreitem{50}{Describe the first guest (at least 4 characteristics) to the second guest}
	
	\scoreheading{Deus Ex Machina}
	\penaltyitem[3]{75}{Alternative HRI}
	% \penaltyitem[3]{200}{Not recognizing people}

	

\end{scorelist}
\clearpage
