\section{Carry My Luggage [Party Host]}
\label{test:carry-my-luggage}

%% robot in the living room
%% operator asks to help with luggage (pointing or saying)
%% the robot picks up the bags or asks to give it to them
%% robot informs when is ready to follow
%% robot starts following
%% avoids object
%% passes through the door
%% avoids people
%% reenters arena

The robot helps the operator to carry some luggage to a car which is parked outside.

\noindent \textbf{Main Goal:} The robot helps the operator to carry a bag to a car parked outside.\\

% This part is related to a bonus
% \noindent \textbf{Optional Goals:}
% \begin{enumerate}[nosep]
% 	\item Re-entering the arena
% 	\item Following the queue on the way back to the arena
% \end{enumerate}

\subsection*{Focus}
This task focuses on \textit{person tracking}, \emph{navigation in unmapped environments}, \emph{social navigation} and \textit{obstacle avoidance}.

\subsection*{Setup}
\begin{itemize}[nosep]
	\item \textbf{Locations}: 
		\begin{itemize}
		 \item The test takes place both inside and outside the \Arena{}.
		 \item The robot starts at a predefined location in the living room.
		\end{itemize}
	\item \textbf{People}: The operator is standing in front of the robot and is pointing at the bag to be carried outside.
	\item \textbf{Objects}: At least two bags are placed near the operator (within a 2m distance and visible to the robot).
\end{itemize}

\subsection*{Procedure}
\begin{enumerate}[nosep]
	\item \textbf{Picking up the bag:} The robot picks up the bag pointed at by the operator, or asks them to handle it to the robot. If the robot picks up the wrong bag and delivers it, it won't score at any stage.
	\item \textbf{Following the operator:} The robot should inform the operator when it is ready to follow them. The operator walks naturally towards the car; after reaching the car, the operator takes the bag back and thanks the robot.
	\item \textbf{Obstacles:} The robot will face 2 obstacles along its way (in arbitrary order):
	\begin{enumerate*}[label=(\alph*)]
	    \item an object on the ground,
% 		\item a small object on the ground,
% 		\item a hard-to-see object,
		\item a crowd of people obstructing the path outside.
% 		\item a small area blocked using retractable barriers.
	\end{enumerate*}
	
	\item \textbf{Re-entering the arena}: The robot returns to the arena, going back in through the entrance.

% This part is related to a bonus
% 	\item \textbf{Optional goals:}
% 	\begin{enumerate}
% 			\item \textbf{Re-entering the arena}: The robot returns to the arena, going back in through the entrance.

% 			\item \textbf{Following the queue:} After the robot has reached the car, a few of the people that formed the crowd obstructing the robot return to the arena in a queue. The robot can decide to join the queue on its way back to the arena, in a manner that appears natural to the people in the queue.
% 	\end{enumerate}


\end{enumerate}


\subsection*{Additional Rules and Remarks}
\begin{enumerate}[nosep]

    \item \textbf{Finding the operator:} The robot can ask for the operator to go through a calibration procedure. This can be done anytime during the path. However with penalties being applied in this case.
    
    \item \textbf{Dropping the bags:} Dropping a bag causes a penalty. The robot can pick it up again or ask for the operator to pick it up for him.
    
    % \item \textbf{Not picking up a bag:} Unability to pick up a dropped bag results in a task failed and 0 points total earned.

	\item \textbf{Car location:} There is no real car outside; instead, a fixed location outside the \Arena{} is designated as a car location.

	\item \textbf{Reaching the car:} The robot can reach the car location only by following the operator (the location is unknown before the test).

	\item \textbf{Deus ex Machina:} Score reductions for human assistance are applied in case the robot loses the operator, and needs to perform some action to find them again. %through:
    % \begin{enumerate}
    %  \item Natural interaction (e.g., waving and calling)
    %  \item Unnatural interaction (e.g., raising both hands and jumping)
    %  \item Touching the robot (e.g., pulling the robot's hand)
    % \end{enumerate}
	%\begin{table}[h]
    %    \begin{tabular}{m{0.8\linewidth} c}
	%		\textbf{Action} & \textbf{Reduction} \\\hline
	%		Handing over the bag to the robot & 100pts \\
	%		Finding the operator while following them: & \\
	%		\hspace{0.5cm}- Natural interaction (e.g. waving and calling) & 100pts \\
	%		\hspace{0.5cm}- Non-natural interaction (e.g. raising both hands and jumping) & 200pts \\
	%		\hspace{0.5cm}- Touching the robot (e.g. pulling the robot's hand) & 400pts \\\hline
	%	\end{tabular}
	%\end{table}
\end{enumerate}


\subsection*{Referee Instructions}

The referees need to:
\begin{itemize}[nosep]
	\item Select one volunteer to act as the operator.
% 	\item Select three to four people to obstruct the robot's path outside and form the queue on the way back to the arena.
    \item Select three to four people to obstruct the robot's path outside.
	\item Choose positions for the bags and assign a bag to the operator.
% 	\item Choose the order of the obstacles that the robot will face outside while following the operator.
    \item Insert the obstacle somewhere in the path.
	\item Designate a location outside as a car location.
% 	\item Designate a location for the queue to form returning into the arena. The queue is composed of the same people that form the crowd.
	\item Mind the robot when it goes outside the \Arena{}.
\end{itemize}

\subsection*{OC Instructions}

2h before test:
\begin{itemize}[nosep]
	\item Select and announce the robot's starting point.
	\item Select which bags will be used in the test.
\end{itemize}

\subsection*{Score Sheet}

The maximum time for this test is 5 minutes.

\begin{scorelist}
	\scoreheading{Main Goal}
% 	\scoreitem{100}{Picking up the correct bag}
    \scoreitem[2]{350}{Picking up each of the bags without human assistance}
	\scoreitem{600}{Following the person to the car}
    \scoreitem{300}{Avoiding the crowd of people obstructing the path}
% 	\scoreitem{50}{Avoiding the small object on the ground}
    \scoreitem{200}{Avoiding the object on the ground}
    \scoreitem{100}{Leaving the arena}
    \scoreitem{100}{Re-entering the arena}
% 	\scoreitem{50}{Avoiding the hard-to-see object}
% 	\scoreitem{50}{Avoiding the area blocked with retractable barriers}
	
	\scoreheading{Bonus rewards}
	\scoreitem{100}{Picking up both bags at once}

% 	\scoreheading{Regular Penalties}
% 	\scoreitem{50}{Dropping the bag}
	\scoreheading{Regular Penalties}
	\penaltyitem{100}{Dropping the bag and picking it up by itself}
	\penaltyitem{200}{Dropping the bag and asking the operator to pick it up}
	\penaltyitem{200}{Rediscovering the operator}
% 	\scoreheading{Deus Ex Machina Penalties}
% 	\penaltyitem{50}{Rediscovering the operator by natural interaction}
% 	\penaltyitem{100}{Rediscovering the operator by unnatural interaction}
% 	\penaltyitem{200}{Rediscovering the operator by direct contact}




	% No longer necessary, computes automatically
	% \setTotalScore{1000}
\end{scorelist}


\clearpage